Equalizer 2.0\\Convergence of a Parallel Rendering Framework

### 2017-04-03 paperIEEE.tex
Add beechnut distribution graphs
git-svn-id: https://dev.ifi.uzh.ch/vmml/svn/Equalizer16@45 db7c848b-7755-4df2-b763-8796797afa52

Furthermore, various applications and frameworks have used \textsf{Equalizer}
for new research in visualization, such as \textsf{RTNeuron}~\cite{HBBES:13}, an
OpenGL renderer for visualizing simulations of neurocortical brain regions;
\textsf{Omegalib}~\cite{Omegalib}, a framework used in the Cave2, extending
\textsf{Equalizer} for hybrid collaborative 2D/3D environments;

visualization for remote sensing data~\cite{LK:09}, bino.

@@

%----------------------------------------------------------------------
\section{Applications}
%----------------------------------------------------------------------

@@

\fig{fSpikesDist} has a significant compression ratio, which reflects in the
results. Futhermore, only a single distributed object is used to transmit the
volume information in one chunk. Compression for this data is benefitial for
transmitting data over a 10Gb/s link (880 MB/s vs 660MB/s raw data
transfer). Buffering has little benefit since the serialization of volume data
is trivial. Buffered compression makes a huge difference, since the compression
cost can be amortized over $n$ nodes, reaching raw data transmission rates of
3.7 GB/s.

\begin{figure*}[ht]\center
  \includegraphics[width=\textwidth]{images/spikesdist}
  \caption{\label{fSpikesDist}Object mapping (left) and data synchronization
    times (middle, detail view right) for the spike volume data set in
    \fig{fVolumes}, right}
\end{figure*}

>>>>

Furthermore, various applications and frameworks have used \textsf{Equalizer}
for new research in visualization. On the application side, \textsf{RTT
Deltagen}, \textsf{Bino}, \textsf{Livre} and \textsf{RTNeuron}~\cite{HBBES:13}
are the most mature examples and are presented in \sref{sApplications}. On the
framework side, \textsf{Omegalib}~\cite{Omegalib}, a framework used in the
Cave2, made significant progress in integrating 2D collaborative workspaces
like \textsf{Sage~2} with 3D immersive content.

visualization for remote sensing data~\cite{LK:09}

@@

%----------------------------------------------------------------------
\section{Applications\label{sApplications}}
%----------------------------------------------------------------------

@@

The spike volume data set shown has a significant compression ratio, which
reflects in the results in \fig{fSpikesDist}. Futhermore, only a single
distributed object is used to transmit the volume information in one chunk.
Compression for this data is benefitial for transmitting data over a 10Gb/s link
even for a single slave process only (970 MB/s vs 570 MB/s raw data transfer).
Buffering has little benefit since the serialization of volume data is trivial.
Buffered compression makes a huge difference, since the compression cost can be
amortized over $n$ nodes, reaching raw data transmission rates of 3.7 GB/s with
the default Snappy compressor and at best 4.4 GB/s with ZStandard at the lowest
compression ratio.

\begin{figure*}[ht]\center
  \includegraphics[width=\textwidth]{images/spikesdist}
  \caption{\label{fSpikesDist}Object mapping (left) and data synchronization
    times (middle, detail view right) for the spike volume data set in
    \fig{fVolumes}, left}
\end{figure*}

\fig{fBeechnutDist}

\begin{figure*}[ht]\center
  \includegraphics[width=\textwidth]{images/beechnutdist}
  \caption{\label{fBeechnutDist}Object mapping (left) and data synchronization
    times (middle, detail view right) for the beechnut volume data set in
    \fig{fVolumes}, right}
\end{figure*}
